Automatic Singing Transcription

### 2023-12-05 report/paper.tex
add specaugment figures

\usepackage[%
backend=biber,
natbib=true,
% style=apa,
style=ieee
]{biblatex}
\addbibresource{references.bib}

@@

\title{Automatic Singing Transcription}
\author{Victor Shan}
\begin{document}
\maketitle
\begin{multicols*}{2}
\begin{abstract}
\end{abstract}

@@

\subsection{Dataset Augmentation}
\subsubsection{SpecAugment}
Due to the lack of datasets, it is more important to make the most of the existing datasets. One
way to do this is to augment the existing datasets. SpecAugment is a series of techniques that
augment the audio spectrogram to improve the performance of ASR models. A frequent intermediate
representation are Mel-Frequency Cepstral Coefficients (MFCC). These are image representations of
energy at certain frequencies on a scale that more closely matches human hearing \citep{MFCC}.
These techniques include time warping, frequency masking and time masking \citep{SpecAugment}.
Time warping is a technique that stretches or compresses the audio spectrogram in the time
dimension. Frequency masking is a technique that masks a random number of frequency channels in
the audio spectrogram. Time masking is a technique that masks a random number of time steps
in the audio spectrogram. These techniques are used to augment the audio spectrogram before it
is fed into the ASR model. \citep{SpecAugment}

@@

On the TED-LIUM dataset, a dataset of TED talks \cite{tedlium3}, WhisperX was able to acheive a
11.8x speedup over Whisper. This is comparable to wav2vec 2.0 which was a 10.3x speedup over
Whisper. However, WhisperX was also able to achieve a WER of 9.7 compared to the 10.5 WER from
Whisper and 19.8 WER from wav2vec 2.0 \citep{whisperX}. This is a significant improvement over
of speed with a slight increase in performance. This is important for AST because it would allow
for faster training and inference times.

For the word alignment task, WhisperX uses an external phoneme alignment approach to generate
word level timestamps using phoneme level timestamps \citep{whisperX}. The external phoneme
alignment model was actually a wav2vec 2.0 model that used Dynamic Time Warping (DTW) \cite{DTW}
to align the phonemes \citep{whisperX}. The first and last phonemes of each word were used to
generate the word level timestamps \citep{whisperX}.

>>>>

\usepackage[
backend=biber,
natbib=true,
% style=apa,
style=ieee
]{biblatex}
\addbibresource{references.bib}

@@

\title{Automatic Singing Transcription}
\author{Victor Shan}

\begin{document}
\maketitle
\begin{multicols*}{2}
\begin{abstract}
\end{abstract}

@@

\subsection{Dataset Augmentation}
\subsubsection{SpecAugment}
Due to the lack of datasets, it is more important to make the most of the existing datasets. One
way to do this is to augment the existing datasets. SpecAugment is a series of techniques that
augment the audio spectrogram to improve the performance of ASR models. A frequent intermediate
representation are Mel-Frequency Cepstral Coefficients (MFCC).

\begin{figure*}
    \centering
    \includegraphics[width=0.4\textwidth]{assets/waveform-to-spectrogram-sing.png}
    \includegraphics[width=0.4\textwidth]{assets/melspectrogram-mfcc.png}
    \caption{Waveform (top left) can be transformed into a spectrogram (bottom left).
    The spectrogram can be transformed to use the Mel scale in Mel Spectrogram (top right,
    only first section shows) which can futher be transformed into a more discrete MFCC.
    Figures inspired by torchaudio \citep{torchAudioFigures}.}
    \label{fig:MFCC}
\end{figure*}

These are image representations of
energy at certain frequencies on a scale that more closely matches human hearing \citep{MFCC}.
These techniques include time warping, frequency masking and time masking \citep{SpecAugment}.
Time warping is a technique that stretches or compresses the audio spectrogram in the time
dimension. Frequency masking is a technique that masks a random number of frequency channels in
the audio spectrogram. Time masking is a technique that masks a random number of time steps
in the audio spectrogram. These techniques are used to augment the audio spectrogram before it
is fed into the ASR model. \citep{SpecAugment}

@@

On the TED-LIUM dataset, a dataset of TED talks \citep{tedlium3}, WhisperX was able to acheive a
11.8x speedup over Whisper. This is comparable to wav2vec 2.0 which was a 10.3x speedup over
Whisper. However, WhisperX was also able to achieve a WER of 9.7 compared to the 10.5 WER from
Whisper and 19.8 WER from wav2vec 2.0 \citep{whisperX}. This is a significant improvement over
of speed with a slight increase in performance. This is important for AST because it would allow
for faster training and inference times.

For the word alignment task, WhisperX uses an external phoneme alignment approach to generate
word level timestamps using phoneme level timestamps \citep{whisperX}. The external phoneme
alignment model was actually a wav2vec 2.0 model that used Dynamic Time Warping (DTW) \citep{DTW}
to align the phonemes \citep{whisperX}. The first and last phonemes of each word were used to
generate the word level timestamps \citep{whisperX}.
